Dependency in Refinement Logics

### 2015-10-18 doc/paper.tex
layout
wordsmithing

All that remains is to give a new definition of the sequencing tactical
$\ThenTac{\tau_1}{\MkFam{\tau}{\alpha}{I}}$ which accounts for this dependency.
In order to do this, we will need to implement an auxiliary judgment
\framebox{$\ThenMultiAux{\MkFam{\tau}{\alpha}{I}}{E}{\Phi}{E'}{\Phi'}$} that
allows us to apply the family of tactics $\MkFam{\tau}{\alpha}{I}$ pointwise to
a proof state, simultaneously propagating refinements rightward through
substitution. This judgment, which presupposes $\IsEquiv{I}{\Dom\Phi}$, is defined
by recursion on the telescope $\Phi$, viewed as a \emph{cons}-list:

@@

The refinement logic for CTT is a sequent calculus with a single form of
judgment, \framebox{$\Seq{\IMode{H}}{\IMode{P}}$}, which means that the
proposition $P$ is true (and functionally so) under the assumptions in the
telescope $H$. The synthesis of this judgment is a hypothetical witness for the
truth or $P$ (or \emph{extract term}) with free variables in $H$.

@@

\begin{gather*}
  \NuprlRule{\DPairIntroRuleNullary}{
    \SeqExt{H}{\TyDPair{A}{x}{B}}{\Tuple{\alpha,\beta}}
  }{
    \begin{array}{l}
      \SeqExt{H}{A}{\alpha}\\
      \SeqExt{H}{\Subst{\alpha}{x}{B}}{\beta}\\
      \SeqExt{H,x:A}{\MemberUnmoded{B}{\TyUniv}}{\gamma(x)}
    \end{array}
  }\\[6pt]
  \NuprlRule{\DPairElimRule{z}}{
    \SeqExt{H,z:\TyDPair{A}{x}{B},J}{C}{
      \Spread{z}{u}{v}{\alpha(u,v)}
    }
  }{
    \SeqExt{H,z:\TyDPair{A}{x}{B},u:A,v:\Subst{u}{x}{B},\Subst{\Tuple{u,v}}{z}{J}}{C}{
      \alpha(u,v)
    }
  }
\end{gather*}

@@

\begin{gather*}
  \NuprlRule{\DFunIntroRule}{
    \SeqExt{H}{\TyDFun{A}{x}{B}}{\Lam{x}{\alpha(x)}}
  }{
    \begin{array}{l}
      \SeqExt{H,x:A}{B}{\alpha(x)}\\
      \SeqExt{H}{\MemberUnmoded{A}{\TyUniv}}{\beta}
    \end{array}
  }\\[6pt]
  \NuprlRule{\DFunElimRule{z}}{
    \SeqExt{
      H,z:\TyDFun{A}{x}{B},J
    }{C}{
      \beta(\Ap{z}{\alpha}, \Ax)
    }
  }{
    \begin{array}{l}
      \SeqExt{H,z:\TyDFun{A}{x}{B}, J}{A}{\alpha}\\
      \SeqExt{
        H,z:\TyDFun{A}{x}{B},%
        y:\Subst{\alpha}{x}{B},%
        p:\EqMemberUnmoded{y}{\Ap{z}{\alpha}}{\Subst{\alpha}{x}{B}}, J
      }{C}{
        \beta(y,p)
      }
    \end{array}
  }
\end{gather*}

>>>>

All that remains is to give a new definition of the sequencing tactical
$\ThenTac{\tau_1}{\MkFam{\tau}{\alpha}{I}}$ which accounts for this dependency.
To this end, we will need to implement an auxiliary judgment
\framebox{$\ThenMultiAux{\MkFam{\tau}{\alpha}{I}}{E}{\Phi}{E'}{\Phi'}$} that
allows us to apply the family of tactics $\MkFam{\tau}{\alpha}{I}$ pointwise to
a proof state, simultaneously propagating refinements rightward through
substitution. This judgment, which presupposes $\IsEquiv{I}{\Dom\Phi}$, is
defined by recursion on the telescope $\Phi$, viewed as a \emph{cons}-list:

@@

The refinement logic for CTT is a sequent calculus with a single form of
judgment, \framebox{$\Seq{\IMode{H}}{\IMode{P}}$}, which means that the
proposition $P$ is true (and functionally so) under the assumptions in the
telescope $H$. The synthesis of this judgment is a hypothetical witness for the
truth or $P$ (or \emph{extract term}) with free variables bound in $H$.

@@

\[
  \begin{array}{l}
    \NuprlRule{\DPairIntroRuleNullary}{
      \SeqExt{H}{\TyDPair{A}{x}{B}}{\Tuple{\alpha,\beta}}
    }{
      \begin{array}{l}
        \SeqExt{H}{A}{\alpha}\\
        \SeqExt{H}{\Subst{\alpha}{x}{B}}{\beta}\\
        \SeqExt{H,x:A}{\MemberUnmoded{B}{\TyUniv}}{\gamma(x)}
      \end{array}
    }\\\\
    \NuprlRule{\DPairElimRule{z}}{
      \SeqExt{H,z:\TyDPair{A}{x}{B},J}{C}{
        \Spread{z}{u}{v}{\alpha(u,v)}
      }
    }{
      \SeqExt{H,z:\TyDPair{A}{x}{B},u:A,v:\Subst{u}{x}{B},\Subst{\Tuple{u,v}}{z}{J}}{C}{
        \alpha(u,v)
      }
    }
  \end{array}
\]

@@

\[
  \begin{array}{l}
    \NuprlRule{\DFunIntroRule}{
      \SeqExt{H}{\TyDFun{A}{x}{B}}{\Lam{x}{\alpha(x)}}
    }{
      \begin{array}{l}
        \SeqExt{H,x:A}{B}{\alpha(x)}\\
        \SeqExt{H}{\MemberUnmoded{A}{\TyUniv}}{\beta}
      \end{array}
    }\\\\
    \NuprlRule{\DFunElimRule{z}}{
      \SeqExt{
        H,z:\TyDFun{A}{x}{B},J
      }{C}{
        \beta(\Ap{z}{\alpha}, \Ax)
      }
    }{
      \begin{array}{l}
        \SeqExt{H,z:\TyDFun{A}{x}{B}, J}{A}{\alpha}\\
        \SeqExt{
          H,z:\TyDFun{A}{x}{B},%
          y:\Subst{\alpha}{x}{B},%
          p:\EqMemberUnmoded{y}{\Ap{z}{\alpha}}{\Subst{\alpha}{x}{B}}, J
        }{C}{
          \beta(y,p)
        }
      \end{array}
    }
  \end{array}
\]
